---
title: "DataExplorationAssignment"
author: "Natasha, Jill, Erik"
date: '2023-02-24'
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fixest)
library(vtable)
library(scales)
library(plotly)
library(shiny)
library(ggiraph)
library(dygraphs)
library(htmlwidgets)
library(lubridate)
```
# Variable Decriptions

| Base Data Set Variable |  Definition
|:------    |:-------------------------------------------------     | 
| `Year`  | The calendar year  |
| `Name`  | state Name  |
| `FYEndingDate`  | state end of fiscal year date  |
| `PropertyTax`  | When the order was placed  |
| `a`  | The Zip code where the order was delivered  |
| `b`  | The State where the order delivered  |
| `c`  | The City where the order was delivered  |
| `d`  | Which is the population in that ZIP code  |
| `e`  |  median annual household income in that ZIP |
| `f`  | which is the annual per-capita income in that ZIP |
| `g`  | the median age of people in the ZIP code  |
| `h`  |  number of people of each broad-category race in ZIP code. |
| `i`  | number of people who are Hispanic in the ZIP code |
| `j`  | which is the number of US citizens living in the ZIP code  |

```{r, echo=TRUE}
df_2021 <- read.table(file = "2021_state_tax.txt", header = TRUE, sep = ",")
vtable(df, lush = TRUE)

```

# 2021 Tax Information Only
```{r, echo=TRUE}
# df_2021 <- df_2021 %>% 
#   mutate(item = case_when(item == 'T01' ~ 'PropertyTaxes', 
#                           item == 'T09' ~ 'GeneralSalesAndGrossReceiptsTax', 
#                           item == 'T10' ~ 'AlcoholBeveragesSalesTax', 
#                           item == 'T11' ~ 'AmusementsSalesTax', 
#                           item == 'T12' ~ 'InsurancePremiumsSalesTax',
#                           item == 'T13' ~ 'MotorFuelsSalesTax',
#                           item == 'T14' ~ 'PariMutuelsSalesTax',
#                           item == 'T15' ~ 'PublicUtilitiesSalesTax',
#                           item == 'T16' ~ 'TobaccoProductsSalesTax', 
#                           item == 'T19' ~ 'OtherSelectiveSalesAndGrossReceiptsTaxes',
#                           item == 'T20' ~ 'AlcoholicBeverageLicense', 
#                           item == 'T21' ~ 'AmusementsLicense',
#                           item == 'T22' ~ 'CorporationInGeneralLicense',
#                           item == 'T23' ~ 'HuntingAndFishingLicense',
#                           item == 'T24' ~ 'MotorVehicleLicensing',
#                           item == 'T25' ~ 'MotorVehicleOperatorsLicense',
#                           item == 'T27' ~ 'PublicUtilitiesLicense',
#                           item == 'T28' ~ 'OccupationAndBusinessLicense',
#                           item == 'T29' ~ 'OtherLicenseTaxes',
#                           item == 'T40' ~ 'IndividualIncomeTaxes',
#                           item == 'T41' ~ 'CorporationNetIncomeTaxes',
#                           item == 'T50' ~ 'DeathAndGiftTaxes',
#                           item == 'T51' ~ 'DocumentaryAndStockTransferTaxes',
#                           item == 'T53' ~ 'SeveranceTaxes',
#                           item == 'T99' ~ 'TaxesNEC')
#          ) 
#   
# 
# vtable(data, lush = TRUE)
```

# Historical Database - 1942 (missing some years) -to-present
```{r, echo=TRUE}
taxes <- read_csv('STC_Historical_DB.csv') %>%
  mutate(StateName = as.factor(Name)) %>%
  select(-State, -Name)
#summary(taxes)
vtable(taxes, lush = TRUE)
```

```{r}
income_tax <- taxes %>%
  select(Year, StateName, `IndividualIncomeTax(T40)`) %>%
  mutate(IndividualIncomeTax = as.numeric(`IndividualIncomeTax(T40)`)) %>%
  group_by(Year)
 
vtable(income_tax, lush = TRUE)


```




```{r}
taxes1 <- taxes %>%
   mutate(`PropertyTax(T01)` = as.numeric(`PropertyTax(T01)`),
         `TotalGenSalesTax(T09)` = as.numeric(`TotalGenSalesTax(T09)`),
         `AmusementTax(T11)` = as.numeric(`AmusementTax(T11)`),
         `ParimutuelsTax(T14)` = as.numeric(`ParimutuelsTax(T14)`),
         `PublicUtilityTax(T15)` = as.numeric(`PublicUtilityTax(T15)`),
         `AlcoholicBeverageLic(T20)` = as.numeric(`AlcoholicBeverageLic(T20)`),
         `AmusementLicense T21)` = as.numeric(`AmusementLicense T21)`),
         `CorporationLicense(T22)` = as.numeric(`CorporationLicense(T22)`),
         `MotorVehOperLicense(T25)` = as.numeric(`MotorVehOperLicense(T25)`),
         `PublicUtilityLicense(T27)` = as.numeric(`PublicUtilityLicense(T27)`),
         `IndividualIncomeTax(T40)` = as.numeric(`IndividualIncomeTax(T40)`),
         `CorpNetIncomeTax(T41)` = as.numeric(`CorpNetIncomeTax(T41)`),
         `DeathANDGiftTax(T50)` = as.numeric(`DeathANDGiftTax(T50)`),
         `DocumumentaryAndStockTransferTax(T51)`= 
                            as.numeric(`DocumumentaryAndStockTransferTax(T51)`),
         `SeveranceTax(T53)` = as.numeric(`SeveranceTax(T53)`),
         `TaxesNEC(T99)` = as.numeric(`TaxesNEC(T99)`)
         #Year = as.Date(paste(Year, 1, 1, sep = "-"))
        ) %>%
  filter(StateName == c('Washington', 'California', 'New York', 'Texas')) %>%
  group_by(Year, StateName, `IndividualIncomeTax(T40)`) %>%
  summarize(Totaltax = sum(`IndividualIncomeTax(T40)`))
vtable(taxes1, lush = TRUE)
```


# Historical Database - DATE CLASS CHANGED TO DATE - 1942 (missing some years) -to-present
```{r, echo=TRUE}
taxes1 <- read_csv('STC_Historical_DB.csv') %>%
  mutate(StateName = as.factor(Name)) %>%
  select(-State, -Name) %>%
   mutate(`PropertyTax(T01)` = as.numeric(`PropertyTax(T01)`),
         `TotalGenSalesTax(T09)` = as.numeric(`TotalGenSalesTax(T09)`),
         `AmusementTax(T11)` = as.numeric(`AmusementTax(T11)`),
         `ParimutuelsTax(T14)` = as.numeric(`ParimutuelsTax(T14)`),
         `PublicUtilityTax(T15)` = as.numeric(`PublicUtilityTax(T15)`),
         `AlcoholicBeverageLic(T20)` = as.numeric(`AlcoholicBeverageLic(T20)`),
         `AmusementLicense T21)` = as.numeric(`AmusementLicense T21)`),
         `CorporationLicense(T22)` = as.numeric(`CorporationLicense(T22)`),
         `MotorVehOperLicense(T25)` = as.numeric(`MotorVehOperLicense(T25)`),
         `PublicUtilityLicense(T27)` = as.numeric(`PublicUtilityLicense(T27)`),
         `IndividualIncomeTax(T40)` = as.numeric(`IndividualIncomeTax(T40)`),
         `CorpNetIncomeTax(T41)` = as.numeric(`CorpNetIncomeTax(T41)`),
         `DeathANDGiftTax(T50)` = as.numeric(`DeathANDGiftTax(T50)`),
         `DocumumentaryAndStockTransferTax(T51)`= 
                            as.numeric(`DocumumentaryAndStockTransferTax(T51)`),
         `SeveranceTax(T53)` = as.numeric(`SeveranceTax(T53)`),
         `TaxesNEC(T99)` = as.numeric(`TaxesNEC(T99)`),
         Year = as.Date(paste(Year, 1, 1, sep = "-"))
        )
vtable(taxes, lush = TRUE)
```




# Population df
```{r, echo=TRUE}
population <- read_csv("population.csv")
vtable(population, lush = TRUE)
```

# Joining Taxes df with population df - Have N/A's introduced and need to fix
```{r}
df <- taxes %>%
  left_join(population, by = "State") %>%
  mutate(Year = as.Date(paste(Year, 1, 1, sep = "-")),
         Name = as.factor(Name), `PropertyTax(T01)` = as.numeric(`PropertyTax(T01)`),
         `TotalGenSalesTax(T09)` = as.numeric(`TotalGenSalesTax(T09)`),
         `AmusementTax(T11)` = as.numeric(`AmusementTax(T11)`),
         `ParimutuelsTax(T14)` = as.numeric(`ParimutuelsTax(T14)`),
         `PublicUtilityTax(T15)` = as.numeric(`PublicUtilityTax(T15)`),
         `AlcoholicBeverageLic(T20)` = as.numeric(`AlcoholicBeverageLic(T20)`),
         `AmusementLicense T21)` = as.numeric(`AmusementLicense T21)`),
         `CorporationLicense(T22)` = as.numeric(`CorporationLicense(T22)`),
         `MotorVehOperLicense(T25)` = as.numeric(`MotorVehOperLicense(T25)`),
         `PublicUtilityLicense(T27)` = as.numeric(`PublicUtilityLicense(T27)`),
         `IndividualIncomeTax(T40)` = as.numeric(`IndividualIncomeTax(T40)`),
         `CorpNetIncomeTax(T41)` = as.numeric(`CorpNetIncomeTax(T41)`),
         `DeathANDGiftTax(T50)` = as.numeric(`DeathANDGiftTax(T50)`),
         `DocumumentaryAndStockTransferTax(T51)`= 
                            as.numeric(`DocumumentaryAndStockTransferTax(T51)`),
         `SeveranceTax(T53)` = as.numeric(`SeveranceTax(T53)`),
         `TaxesNEC(T99)` = as.numeric(`TaxesNEC(T99)`),
         State = as.factor(State)
         )

vtable(df, lush = TRUE)
```

# Correlation Matrix for Numerical Variables
```{r, echo=TRUE}
eda_corr <- df
eda_corr <- as.data.frame(eda_corr1)
corr_simple <- function(data=eda_corr,sig=0.0){
#convert data to numeric in order to run correlations
#convert to factor first to keep the integrity of the data - each value will become a number rather than turn into NA
df_cor <- eda_corr1 %>% mutate_if(is.character, as.factor)
df_cor <- eda_corr1 %>% mutate_if(is.factor, as.numeric) %>%
                    mutate_if(is.logical, as.numeric)

#run a correlation and drop the insignificant ones
corr <- cor(df_cor)

#prepare to drop duplicates and correlations of 1     
corr[lower.tri(corr,diag=TRUE)] <- NA 

#drop perfect correlations
corr[corr == 1] <- NA 

#turn into a 3-column table
corr <- as.data.frame(as.table(corr))

#remove the NA values from above 
corr <- na.omit(corr) 

#select significant values  
corr <- subset(corr, abs(Freq) > sig) 

#sort by highest correlation
corr <- corr[order(-abs(corr$Freq)),] 

#print table
print(corr)

#turn corr back into matrix in order to plot with corrplot
mtx_corr <- reshape2::acast(corr, Var1~Var2, value.var="Freq")
  
#plot correlations visually
corrplot(mtx_corr, is.corr=FALSE, tl.col="black", na.label=" ")
}
corr_simple()

```






















